Robust Adaptation to Multi-Scale Climate Variability

### 2019-05-18 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
Final tweaks

Despite recent insights, important questions remain.
How should a portfolio of risk mitigation instruments be optimized?
How should one choose between permanent and transient instruments?
Under what conditions is a permanent, large infrastructure investment required, and what information is needed to recognize this threshold?
In this paper we focus \add{more narrowly on the temporal}\remove{ on the narrower question of how the temporal} structure of climate risk, and the uncertainties associated with its estimation, influence the answers to these questions.
We continue this section with three specific observations about climate risk which, while seemingly obvious, have important and subtle implications that we examine in \cref{sec:methods,sec:results,sec:discussion-conclusions}.

@@

Public or private sector investments in climate adaptation require not only the design of each potential structural instrument, but also selecting between instruments with vastly different operational planning periods.
This project planning period, which we define as being $M$ years, describes the nominal economic or physical lifespan of the structure or contract.
Typical planning periods may vary from $M=1$ year or less for a financial contract to $M=100$ years or longer for a structural instrument, as illustrated in \cref{tab:real-world-M}.
The planning period can also be interpreted as the finite period over which \gls{cba} is conducted when assessing the project.

>>>>

Despite recent insights, important questions remain.
How should a portfolio of risk mitigation instruments be optimized?
How should one choose between permanent and transient instruments?
Under what conditions is a permanent, large infrastructure investment required, and what information is needed to recognize this threshold?
In this paper we focus \add{more narrowly on the temporal}\remove{ on the narrower question of how the temporal} structure of climate risk and \add{how} the uncertainty associated with its estimation\remove{,} influence\add{s} the answers to these questions.
We continue this section with three specific observations about climate risk which, while seemingly obvious, have important and subtle implications that we examine in \cref{sec:methods,sec:results,sec:discussion-conclusions}.

@@

Public or private sector investments in climate adaptation require not only the design of each potential\remove{structural} instrument, but also selecting between instruments with vastly different operational planning periods.
This project planning period, which we define as being $M$ years, describes the nominal economic or physical lifespan of the structure or contract.
Typical planning periods may vary from $M=1$ year or less for a financial contract to $M=100$ years or longer for a structural instrument, as illustrated in \cref{tab:real-world-M}.
The planning period can also be interpreted as the finite period over which \gls{cba} is conducted when assessing the project.
